Evaluating approaches to deriving photometric redshift posterior probability distribution functions for \textsc{LSST}

### 2019-03-09 paper/tex/introduction.tex
typo

There are numerous techniques for deriving \pzpdf s, yet no one method has yet been established as clearly superior.
Quantitative comparisons of photo-$z$ methods have been made before.
The Photo-$z$ Accuracy And Testing \citep[\textsc{PHAT},][]{Hildebrandt:10} effort focused on \pz\ point estimates derived from many photometric bands.
\citet{Rau:2015} introduced a new method for improving \pzpdf s using an ordinal classification algorithm.
\textsc{DES} compared several codes for \pz\ point estimates and a subset with \pzpdf\ information \citep{Sanchez:14} and examined summary statistics of \pzpdf s for tomographically binned galaxy subsamples \citep{Bonnett:16}.

>>>>

There are numerous techniques for deriving \pzpdf s, yet no one method has yet been established as clearly superior.
Quantitative comparisons of \pz\ methods have been made before.
The \Pz\ Accuracy And Testing \citep[\textsc{PHAT},][]{Hildebrandt:10} effort focused on \pz\ point estimates derived from many photometric bands.
\citet{Rau:2015} introduced a new method for improving \pzpdf s using an ordinal classification algorithm.
\textsc{DES} compared several codes for \pz\ point estimates and a subset with \pzpdf\ information \citep{Sanchez:14} and examined summary statistics of \pzpdf s for tomographically binned galaxy subsamples \citep{Bonnett:16}.
